Check experimental design

### 2021-10-18 analysis/01_experimental-design.Rmd
Cleaned up dummy coding, removed index coding, and built out interactions for the design

# Use the output of lm to get a dummy-coded version of the design
dummy_design$y <- matrix(rnorm(nrow(dummy_design)), ncol=1)
out <- lm(y ~ ., dummy_design, x = TRUE)
dummy_design <- out$x[,-1]
rownames(dummy_design) <- NULL

@@

>>>>

# Use dummy_cols() to get a index-coded version of all the attribute levels.
dummy_design <- dummy_cols(
  dummy_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
)

# Rename the index variables.
colnames(dummy_design)[4:15] <- c(
  str_c("org", 2:4), str_c("issue", 2:4), str_c("transp", 2),
  str_c("account", 2), str_c("fund", 2:3), str_c("gov_rel", 2:3)
)

@@

# Interact-code the design

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need a specific intercept-only design with each of the needed interactions.

```{r interact-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interact_design <- as.data.frame(design)
for(i in 4:ncol(interact_design)) {
  interact_design[,i] <- as.factor(interact_design[,i])
}

# Rename the variables.
colnames(interact_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
interact_design <- dummy_cols(
  interact_design, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables.
colnames(interact_design)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions.
interact_design %>% 
  as_tibble() %>% 
  mutate(
    # Hypothesis 2b.
    amnesty_criticized = org1 * gov_rel2,
    amnesty_crackdown = org1 * gov_rel3,
    greenpeace_criticized = org2 * gov_rel2,
    greenpeace_crackdown = org2 * gov_rel3,
    oxfam_criticized = org3 * gov_rel2,
    oxfam_crackdown = org3 * gov_rel3,
    redcross_criticized = org4 * gov_rel2,
    redcross_crackdown = org4 * gov_rel3,
    # Hypothesis 3b.
    emergency_criticized = issue1 * gov_rel2,
    emergency_crackdown = issue1 * gov_rel3,
    environment_criticized = issue2 * gov_rel2,
    environment_crackdown = issue2 * gov_rel3,
    humanrights_criticized = issue3 * gov_rel2,
    humanrights_crackdown = issue3 * gov_rel3,
    refugees_criticized = issue4 * gov_rel2,
    refugees_crackdown = issue4 * gov_rel3,
    # Hypothesis 4b.
    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,
    wealthydonors_criticized = fund2 * gov_rel2,
    wealthydonors_crackdown = fund2 * gov_rel3,
    govgrants_criticized = fund3 * gov_rel2,
    govgrants_crackdown = fund3 * gov_rel3,
    # Hypothesis 4c.
    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3,
    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
    # Hypothesis 5b.
    transp_criticized = transp1 * gov_rel2,
    transp_crackdown = transp1 * gov_rel3,
    nottransp = ifelse(transp1 == 0, 1, 0),
    nottransp_criticized = nottransp * gov_rel2,
    nottransp_crackdown = nottransp * gov_rel3,
    # Hypothesis 5c.
    transp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    transp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    transp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    transp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    transp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    transp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_smalldonors_criticized = nottransp * fund1 * gov_rel2,
    nottransp_smalldonors_crackdown = nottransp * fund1 * gov_rel3,
    nottransp_wealthydonors_criticized = nottransp * fund2 * gov_rel2,
    nottransp_wealthydonors_crackdown = nottransp * fund2 * gov_rel3,
    nottransp_govgrants_criticized = nottransp * fund3 * gov_rel2,
    nottransp_govgrants_crackdown = nottransp * fund3 * gov_rel3,
    # Hypothesis 5d.
    transp_emergency_criticized = transp1 * issue1 * gov_rel2,
    transp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    transp_environment_criticized = transp1 * issue2 * gov_rel2,
    transp_environment_crackdown = transp1 * issue2 * gov_rel3,
    transp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    transp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    transp_refugees_criticized = transp1 * issue4 * gov_rel2,
    transp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_emergency_criticized = nottransp * issue1 * gov_rel2,
    nottransp_emergency_crackdown = nottransp * issue1 * gov_rel3,
    nottransp_environment_criticized = nottransp * issue2 * gov_rel2,
    nottransp_environment_crackdown = nottransp * issue2 * gov_rel3,
    nottransp_humanrights_criticized = nottransp * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = nottransp * issue3 * gov_rel3,
    nottransp_refugees_criticized = nottransp * issue4 * gov_rel2,
    nottransp_refugees_crackdown = nottransp * issue4 * gov_rel3,
    # Hypothesis 5e.
    transp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    transp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    transp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    transp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    transp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    transp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    transp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    transp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = nottransp * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = nottransp * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = nottransp * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = nottransp * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = nottransp * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = nottransp * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = nottransp * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = nottransp * fund1 * issue4 * gov_rel3
  ) %>% 
  # Drop first levels and the nottransp helper variable.
  select(-c(contains("1"), nottransp))

# Save interact-coded design output
write.csv(interact_design, here("data", "derived_data", "interact_design.csv"))
```
